---
title: "MechaCarChallenge Notebook"
assignment: Challenge 15
author: Samad Fassihi
---
```{r}

```
---
Helpful Commands
 Add new chunk *Cmd+Option+I*
 Preview HTML *Cmd+Shift+K* 
---
```{r}

```
# Set current working directory
setwd("~/Documents/Data Analytics Course/Module 15/AutosRUs Challenge/data ")
```{r}

```
# Import MechaCar raw csv 
MechaCar_mpg <- read.csv('MechaCar_mpg.csv',check.names = F, stringsAsFactors = F)
```{r echo=FALSE, paged.print=TRUE}
head(MechaCar_mpg)
```
# Perform multivariate linear regression to estimate mpg; Return summary statistics
```{r}
summary(lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data = MechaCar_mpg))
```

matrix_coef <- summary(lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data = MechaCar_mpg))$coefficients

```{r}
head(matrix_coef)
```
```{r}

```
# Import Suspension Coil raw data
Suspension_Coil <- read.csv('Suspension_Coil.csv',check.names = F, stringsAsFactors = F)
```{r}
head(Suspension_Coil)
```
# Create summary for dataframe on 'PSI' column using pipe operator
total <- Suspension_Coil %>% summarize(Mean = mean(PSI), Median = median(PSI), Variance = var(PSI), SD = sd(PSI), .groups = 'keep')
```{r}
head(total)
```
# Group by on Manufacturing Lot for lot_summary
lot_summary <- Suspension_Coil %>% group_by(Manufacturing_Lot) %>% summarize(Mean = mean(PSI), Median = median(PSI), Variance = var(PSI), SD = sd(PSI), .groups = 'keep')
```{r}
head(lot_summary)
```
# Perform statistical tests on Manufacturing Lots and determine if are statistically different from the population mean (1500 PSI)
t_test_all <- t.test(Suspension_Coil$PSI, mu = 1500)
```{r}
head(t_test_all$p.value)
```

t_test_lot1 <- t.test(subset(Suspension_Coil, Manufacturing_Lot == 'Lot1')$PSI, mu = 1500)
t_test_lot2 <- t.test(subset(Suspension_Coil, Manufacturing_Lot == 'Lot2')$PSI, mu = 1500)
t_test_lot3 <- t.test(subset(Suspension_Coil, Manufacturing_Lot == 'Lot3')$PSI, mu = 1500)

```{r}
head(t_test_lot1$p.value)
head(t_test_lot2$p.value)
head(t_test_lot3$p.value)


```
plt <- ggplot(Suspension_Coil, aes(x=log10(PSI)))
```{r}
plt + geom_density()

```